Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-15 TitlePage.tex
TitlePage.tex: cleanup cruft, document more

%\pagestyle{empty}
\begin{titlepage}
{

\makeatletter
\centering
% https://tex.stackexchange.com/a/241121/1340
\linespread{1.5}\selectfont
\parskip 0pt
%\sffamily

@@

{\huge \bfseries
  \@title\par}

\vspace{4cm}
\large

{\bfseries Dissertation}\\
%
%\vspace{0.5cm}
%
der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr. rer. nat.)

@@

\vfill
\makeatother
}
\end{titlepage}
% TODO: insert here page 2 with the needed thesis boilerplate.
%\clearpage
% \pagestyle{myheadings}

>>>>

\begin{titlepage}
% Declarations, in scope until \end{titlepage}.
\makeatletter % for \@title and \@author
\setlength{\parskip}{0pt}
\centering
\large
%
% https://tex.stackexchange.com/a/241121/1340
\linespread{1.5}\selectfont
%\sffamily

@@

{\huge \bfseries
  \@title%
  \par% Must be in scope of the \huge declaration to get correct spacing.
}

\vspace{4cm}

{\bfseries Dissertation}\\
der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr. rer. nat.)

@@

\vfill
\end{titlepage}
% TODO: insert here page 2 with the needed thesis boilerplate.
%\clearpage
